A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-03-12 crystal-gel/nature/crystal_gel2.tex
Remove marker for critical point. Swap solid and dashed lines between spinodal and binodal.

\begin{figure*}[!t]
 \centering
 \includegraphics{phase_separation.pdf}
 \caption{{\bf Different routes of viscoelastic phase separation.} 
{\bf a,} Phase diagram. Gray areas are equilibrium fluid and crystal regions. The dashed and continuous lines are the metastable gas-liquid binodal and spinodal respectively. The black diamond marks the critical point. Empty black triangles are experimental point showing a fluid behaviour. The other symbols are the experimental points showing gel behaviour, consistently used in all panels. The dotted lines are the gas-liquid tie lines determined experimentally, with arrow heads indicating measured gas and liquid compositions.
{\bf b,} Radius of gyration ($R_g$) as a function of cluster size ($s$) for all state points at percolation. The
 gray line represents the fractal dimension of the random gelation universality class.
{\bf c,} Structure factors for the late stages of the gelation process. The gray and black lines represents respectively random gelation and compact fractal dimensions.
{\bf d,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle for the state points in the very late stage. Horizontal lines stress the value at 12 neighbours.
 }
 \label{fig:phase_separation}
\end{figure*}

>>>>

\begin{figure*}[!t]
 \centering
 \includegraphics{phase_separation.pdf}
 \caption{{\bf Different routes of viscoelastic phase separation.} 
{\bf a,} Phase diagram. Empty black triangles are experimental point showing a fluid behaviour. The other symbols are the experimental points showing gel behaviour, consistently used in all panels. The dotted lines are the gas-liquid tie lines determined experimentally, with arrow heads indicating measured gas and liquid compositions. Gray areas are theoretical equilibrium fluid and crystal regions. The solid and dashed lines are the metastable gas-liquid binodal and spinodal respectively.
{\bf b,} Radius of gyration ($R_g$) as a function of cluster size ($s$) for all state points at percolation. The
 gray line represents the fractal dimension of the random gelation universality class.
{\bf c,} Structure factors for the late stages of the gelation process. The gray and black lines represents respectively random gelation and compact fractal dimensions.
{\bf d,} Local volume fraction around a colloidal particle, as a function of the number of nearest neighbours of the particle for the state points in the very late stage. Horizontal lines stress the value at 12 neighbours.
 }
 \label{fig:phase_separation}
\end{figure*}
